\documentclass[10pt,a4paper]{moderncv/moderncv}

\moderncvstyle{classic}       % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont[BoldFont=Myriad Pro Bold, ItalicFont=Myriad Pro Italic]{Myriad Pro}
% \setmainfont{Noto Sans}
\setmonofont{Menlo}
\setsansfont{Arial}

\usepackage[us]{datetime}
\usepackage{footmisc} % enabling footnotes.
\makeatletter
\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

\usepackage[scale=0.72]{geometry}  % adjust the page margins
\recomputelengths                  % required when changes are made to page layout lengths

% personal data
\firstname{\textbf{Pei}}
\familyname{\textbf{QING}}
\email{hello@qingpei.me}
%\email{edward.qing@gmail.com}
%\email{edwardtoday@gmail.com}
\phone[mobile]{+86 186-2111-0317}


\social[github]{edwardtoday}
\homepage{https://www.qingpei.me}

% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

% \nopagenumbers{}            % uncomment to suppress automatic page numbering for CVs longer than one page

\begin{document}
\maketitle


%\section{Objective}
%\cvitem{Software Devoloper}{Networking, Data Processing}

\section{Education}
\cventry{2011--2012}{M.Sc. in Software Technology}{The Hong Kong Polytechnic University}{}{GPA:3.95/4 with Distinction}{}
\cventry{2006--2010}{B.Eng. in Computer Science and Technology}{Tsinghua University}{Beijing}{GPA:85/100}{}
\cventry{2007--2010}{B.S. in Economics}{Tsinghua University}{Beijing}{dual degree}{}

\section{Working Experience}
\cventry{2013--present}{Software Engineer}{Shanghai Sansi Technology Co., Ltd.}{Shanghai}{}
{
\begin{itemize}
	\item Smart bulb iOS app. First working demo in 32 days including learning Objective-C for 2 weeks.
	\item Networking module of LED display/lamp control system. Unified interface for TCP/UDP/RS-485 controllers. \textbf{6X higher throughput} than previous version by asynchronous design.
	\item Display calibration toolkit optimization. \textbf{30X faster} pixel searching. Better perceived uniformity.
	\item Advocated the adoption of Git, GitLab \& Redmine within the group.
	\item Converted 9 low-utilization physical servers to a more maintainable virtual machine.
\end{itemize}
}

\cventry{2012--2013}{Research Assistant}{Biometrics Research Center, The Hong Kong Polytechnic University}{}{}
{
\begin{description}
	\item[Data Source:] Samples of pulse, electrocardiogram, tongue photo, front face photo and breath composition analysis results from both healthy and diabetes people.
	\item[Objective:] To discover if some disease (diabetes in this case) has strong correlation with multiple physical signs of human body. Build a diagnosis model bases on the correlation to improve accuracy and consistency of diagnoses.
	\item[Methodology:] Iterations of ``Feature Extraction $\rightarrow$ Fusion of Multiple Features $\rightarrow$ Feature Optimization $\rightarrow$ Machine Learning $\rightarrow$ Model Simplification'' process.
	\item[Current Status:]  We achieved an \textbf{accuracy of 97.1\%} of diabetes diagnosis. By contrast, the accuracy using a single source of physical signs were 65\% to 90\%. Thus we have lowered the mis-diagnosis rate by roughly an order of magnitude.
\end{description}
}

\cventry{2010--2011}{Software Developer}{Virtuos Games}{Shanghai}{}
{
\begin{itemize}
	\item Architected and implemented a cross-platform game for PC/Mac/iPhone/iPad. Optimized the graphics performance from \textbf{14FPS to 31FPS} on iPhone 4.
	\item Designed synchronization tool with C++/Python to support inter-department process.
	% \item Acted as communicator between Technical and Art department to smooth out interdepartmental tasks.
	% \item Acted as technical leader of internal iOS project. My demonstration attracted 3 clients to sign contracts with Virtuos on new iOS projects.
\end{itemize}
}

%\cventry{2009}{Intern Programmer}{Endress+Hauser}{Shanghai}{}
%{
%\begin{itemize}
%	\item Designed 3D models with Modo to present previews of customized products.
%	\item Proposed and designed a product customization software with dynamic help for each part.
%\end{itemize}
%}

\cventry{2008}{Volunteer, Assistant Officer}{International Broadcast Center, $29$th Olympic Games}
{Beijing}{}
{
\begin{itemize}
	\item Collected needs from agents of different media. Contact officers from inside IBC to meet their needs, or turn to Director for request necessary resources.
	\item Administrated attendance system of the venue, sending daily report on venue operations status.
\end{itemize}
}

%\cventry{2007-2009}{Vice Director, Director}{Liaison Department, Student Union of Dept., Tsinghua University}
%{Beijing}{}
%{
%\begin{itemize}
%	\item Coordinated actions on seeking sponsors for student activities.
%	\item Raised money for freshman orientation party.
%\end{itemize}
%}

\section{Personal Projects}

\cventry{2013}
{image-converter-for-kindle: Convert JPEG images to kindle screensavers}
{Python}
{}{}
{
Resize, crop, rotate and optimize images for the e-ink screen on Kindle.
}

\cventry{2013}
{mymaxim: Show random maxim in my blog posts}
{Javascript}
{}{}
{
A script that shows random maxims on my personal site.
}

\cventry{2012}
{hkputhesis: The Hong Kong Polytechnic University M.Sc. thesis latex template}
{\LaTeX}
{}{}
{
No one has ever made such a template for HKPU thesis. While I was writing my M.Sc. dissertation, I wrote the template and open-sourced it in case someone needed them in the future.
}

\cventry{2011--2012}
{3D Palm-print Recognition}
{MATLAB}
{}{}
{
\begin{itemize}
	\item Achieved a \textbf{worldwide leading 98.7\%} identification accuracy using 3D palm-print features. (Accuracies found in previous literature were less than 93\%.)
	\item 2X speedup (compared to searching sorted database) gained by utilizing 3D global feature index.
\end{itemize}
}

\cventry{2010}
{Real-time Parallel Decoding of Multi-view Video}
{C++}
{Adviser: Lifeng Sun}{\textit{Scoring 93/100, top 10\%}}
{
\begin{itemize}
	\item Involved in the scheduling algorithm design for dual-view to 8-view MVC video.
	\item Assisted to implement a MVC enc/decoding tool, focusing on the decoding.
	\item Designed and implemented a 3D MVC player on the NVIDIA 3D Vision platform.
	\item Adopted by CCTV to provide experimental 3D online broadcasting of the 2010 Asian Games.
\end{itemize}
}

\cventry{2010}
{MIPS CPU Simulator}
{Java}
{}{}
{
\begin{itemize}
	\item A simulator that reads assembly code and illustrates how a MIPS CPU executes it.
	\item States of all registers and memory spaces can be shown.
\end{itemize}
}

%\cventry{2009}
%{Intelligent Video Processing}
%{C++}
%{}{}
%{
%\begin{itemize}
%	\item Implemented mean shift, GrabCut as pre-processors in the image processing chain.
%	\item Modified GrabCut by replacing user interaction with edge detection to achieve automatic object library creation.
%	\item Gave presentations in weekly discussion on the following paper: ARDECO, Interactive Video Cutout, Photo Clip Art, Video Object Cut and Paste.
%\end{itemize}
%}

\cventry{2009}
{Ray-tracing Renderer and Mesh Simplification}
{C++}
{Computer Graphics course project}{ranked 6/90+ students}
{{
\begin{itemize}
	\item Implemented a C++ ray-tracing renderer with Phong model.
	\item \textbf{Top 10\%} by rendering speed in class.
	\item Implemented both vertex decimation and edge contraction algorithms to simplify a mesh to a customizable complexity.
	\item Provided real-time preview of simplification progress with OpenGL.
\end{itemize}}
}

% \cventry{2009}
% {PhoneMe: A cross-platform address book}
% {Java}
% {Software Engineering course project}{ranked 2/50+ students}
% {
% \begin{itemize}
% 	\item Drafted and maintained requirements, design and technical document.
% 	\item Committed 30\% code of the 16,000-line project.
% 	\item Allocated tasks to team members weekly and tracked daily progress and issues.
% 	\item Held project discussion weekly to minimize mis-communication costs among members.
% 	\item Worked as a team leader.
% \end{itemize}
% }

% \cventry{2009}
% {Simple FTP Client and Server}
% {C++}
% {}{}
% {
% Implemented a lite FTP server and a client with C++ socket.
% }

\cventry{2008}
{16-bit FPGA MIPS CPU}
{VHDL}
{}{}
{
\begin{itemize}
	\item Designed a five-step pipelining structure.
	\item Implemented a processor in VHDL.
	\item Drove several peripherals including audio and video output.
	\item Processor frequency can be up to 50MHz on Cyclone II FPGA.
	\item Worked as a team leader.
\end{itemize}
}

% \cventry{2008}
% {Mine Sweeper on FPGA}
% {VHDL}
% {}{}
% {
% Implemented a mine sweeper game on FPGA platform with mouse, keyboard and VGA controllers included.
% }


% Publications from a BibTeX file without multibib
% to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}       % 'publications' is the name of a BibTeX file

\section{Skills}
\cvitem{Programming}{Used in Working: C++, Objective-C, MATLAB, \LaTeX. Used in Personal Code: Python, Java, R}
\cvitem{Keynote}{Proficient in making readable and clear slides using Apple Keynote or Microsoft PowerPoint. Experienced in delivering presentations.}
\cvitem{Data Analyzing}{Good at computer aided data analysis tools such as Excel, GNU R. Able to write programs to process and interpret data.}
\cvitem{English}{Fluent in spoken and written English, CET-6 652, TOEFL 107}
%\cvitem{Zhihu}{\url{zhihu.com/people/qingpei}, My questions and answers. (Chinese version of Quora)}

% \section{Awards}
% \cventry{2009}{Outstanding Student Leaders in Department of Computer Science and Technology}{Tsinghua University}{}{}{}
% \cventry{2008}{Excellent Volunteer at International Broadcast Center (IBC)}{The Beijing Organizing Committee for the Games of the XXIX Olympiad}{}{}{}
% \cventry{2006}{First Prize in Haiwen Cup Shanghai High-school English Competition}{Shanghai Municipal Education Commission}{}{}{}
% \cventry{2004}{Second Prize in "21st Century Cup" National English Speaking Contest}{Foreign Language Teaching and Research Press}{}{}{}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\vfill
\enlargethispage{\footskip}
\blfootnote{Last updated: \today}

%\clearpage
%%-----       letter       ---------------------------------------------------------
%% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{\today}
%\opening{Dear Sir or Madam,}
%\closing{Respectfully yours,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%
%Body of Cover Letter
%
%The body of your cover letter lets the employer know what position you are applying for, why the employer should select you for an interview, and how you will follow-up.
%
%First Paragraph:
%
%The first paragraph of your letter should include information on why you are writing. Mention the position you are applying for. Include the name of a mutual contact, if you have one. Be clear and concise regarding your request. Convince the reader that they should grant the interview or appointment you requested in the first paragraph.
%
%Middle Paragraphs:
%
%The next section of your cover letter should describe what you have to offer the employer. Make strong connections between your abilities and their needs. Mention specifically how your skills and experience match the job you are applying for. Remember, you are interpreting your resume, not repeating it. Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text.
%
%Final Paragraph:
%
%Conclude your cover letter by thanking the employer for considering you for the position. Include information on how you will follow-up. State that you will do so and indicate when (one week's time is typical). You may want to reduce the time between sending out your resume and follow up if you fax or e-mail it.
%
%\makeletterclosing

\end{document}
